UKB Models

### 2023-10-02 ukb_mods.Rmd
global CT and SA values for better global correction

skim(ukb_df)
n_unique(ukb_df$participant) == nrow(ukb_df) #no duplicate subj

#write data
write_csv(ukb_df, file="data/ukb_CN_data.csv")

col_list <- colnames(ukb_df)
pheno_list <- col_list[grepl("^lh_|^rh_|^GMV$|^WMV$|^sGMV$|^Ventricles$", col_list)]
writeLines(pheno_list, con = "phenotype_list.txt")
```

@@

>>>>

skim(ukb_df)
n_unique(ukb_df$participant) == nrow(ukb_df) #no duplicate subj
```

Write lists of phenotypes

```{r}
col_list <- colnames(ukb_df)
pheno_list <- col_list[grepl("^lh_|^rh_|^GMV$|^WMV$|^sGMV$|^Ventricles$", col_list)]
length(pheno_list) #total number of models to run

#split by measure type (Vol, SA, CT)
vol_list <- col_list[grepl("^lh_Vol|^rh_Vol|^GMV$|^WMV$|^sGMV$|^Ventricles$", col_list)]
writeLines(vol_list, con = "pheno_lists/Vol_list.txt")

sa_list <- col_list[grepl("^lh_SA|^rh_SA", col_list)]
writeLines(sa_list, con = "pheno_lists/SA_list.txt")

ct_list <- col_list[grepl("^lh_CT|^rh_CT", col_list)]
writeLines(ct_list, con = "pheno_lists/CT_list.txt")
```

Add brainwide phenotypes!
Summing across regions for volumes (rather than summing GMV, sGMV, etc) for consistency with SA and CT

```{r}
vol_list_regions <- col_list[grepl("^lh_Vol|^rh_Vol", col_list)]

ukb_df_totals <- ukb_df %>%
  mutate(Vol_total=rowSums(select(., .dots=all_of(c(vol_list_regions)))),
         SA_total=rowSums(select(., .dots=all_of(c(sa_list)))),
         CT_total=rowSums(select(., .dots=all_of(c(ct_list)))))

#write data
write_csv(ukb_df_totals, file="data/ukb_CN_data.csv")
```

@@

# CUBIC Models
Playing around wiht models fit on cubic using `fit_ukb_mod.R`

scp-ing random model to look at (`lh_SA_middletemporal_mod.rds`)

```{r}
lh_SA_middletemporal_mod <- readRDS("ukb/gamlss_objs/lh_SA_middletemporal_mod.rds")
summary(lh_SA_middletemporal_mod)

```
